---
title: "Pupping grounds"
# author: "Lotte Pohl"
execute:
  echo: false
  include: false
output:
  html_document:
    df_print: paged
    theme: readable
    # toc_float: true
    toc: true
    # number_sections: false
    # toc_depth: 2
subtitle: master thesis Lotte Pohl, progress 3.3.2023
editor_options:
  chunk_output_type: console
knitr:
  opts_chunk: 
    collapse: true
format: 
  html:
    page-layout: article
    code-tools: true
    fig-width: 8
    fig-height: 5
    toc: true
---

```{r libraries}
library(tidyverse)
library(lubridate)
library(leaflet)
library(tibble)
library(stringr)
library(ggsci)
library(pander)
library(mregions2)
library(fuzzyjoin)
library(sf)
library(plotly)
library("FactoMineR")
library("factoextra")
library(knitr)
library(quarto)
library(car)

```


```{r workspace}
rm(list = ls())
dir_path <- "C:/Users/lotte.pohl/Documents/github_repos/ADST_Mustelus_asterias"
# path_envdata <- paste0(dir_path, "/03_data/environmental_layers/")
# path_boundaries <- paste0(dir_path, "/03_data/marine_boundaries/")
source(paste0(dir_path, "/functions.R"))
# source(paste0(dir_path, "/functions/functions_DST_presstemplogs.R"))
# make into file in `wrangle_data` folder
# source(paste0(dir_path, "/02_scripts/02_load_data/load_environmental_data.R"))
# source(paste0(dir_path, "/02_scripts/02_load_data/load_human_activities.R"))
# source(paste0(dir_path, "/02_scripts/02_load_data/load_marine_boundaries.R"))
# source(paste0(dir_path, "/02_scripts/03_wrangle_data/wrangle_acoustic_data.R"))

# load analysis
source(paste0(dir_path, "/02_scripts/04_analyses/pupping_grounds/investigation_acoustic_data_females.R"))
```


### Pupping area investigation: acoustic data

> Question 1: Can we see similar behaviour in acoustic detections of female sharks in close to Dishoek to what we saw in the DST data from shark 308?

> Question 2: For sharks that were detected in the WS1 area in 2 consecutive summers, can we see differing behaviour (given that the species only gives birth every other year)?

## Method

I looked at all females detected in the WS and grouped their detection per station and day.

## Results
### tags with many data

:::{.panel-tabset}

#### tag 297
```{r tag297}
#| layout-nrow: 1
#| include: true
map_acoustic_297_2018
map_acoustic_297_2019
```

#### tag 299
```{r tag299}
#| layout-nrow: 1
#| include: true
map_acoustic_299_2018
map_acoustic_299_2019
```

#### tag 300
```{r tag300}
#| layout-nrow: 1
#| include: true
map_acoustic_300
```

#### tag 303
```{r tag303}
#| layout-nrow: 1
#| include: true
map_acoustic_303
```

#### tag 307
```{r tag307}
#| layout-nrow: 1
#| include: true
map_acoustic_307_2018
map_acoustic_307_2019
```

#### tag 308
```{r tag308}
#| layout-nrow: 1
#| include: true
map_acoustic_308
```

#### tag 313
```{r tag313}
#| layout-nrow: 1
#| include: true
map_acoustic_313_2019
map_acoustic_313_2020
```
:::

### tags with few data

:::{.panel-tabset}

#### tag 298
```{r tag298}
#| layout-nrow: 1
#| include: true
map_acoustic_298
```

#### tag 302
```{r tag302}
#| layout-nrow: 1
#| include: true
map_acoustic_302
```

#### tag 318
```{r tag318}
#| layout-nrow: 1
#| include: true
map_acoustic_318
```
:::